Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-10-04 manuscript.Rmd

```{r Figure 1 Boxplot of Article Counts}

ggplot(data=n.so.yr, aes(x=index, y=n)) +
  stat_boxplot(geom="errorbar")+
  geom_boxplot(outlier.size = 2)+
  ylab("Cumulative article count") +
  annotate("text", x = 0.87, y = 1600, label = "Families in Society")+
  annotate("text", x = 0.91, y = 1400, label = "Social Work") +
  annotate("text", x = 1.20, y = 1350, label = "British Journal of Social Work")+
  theme_bw()+
  theme(axis.title.x = element_blank()) +
  theme(panel.border = element_blank(), axis.line = element_line())+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_x_discrete(breaks=NULL)+
  theme(plot.title = element_text(size = 18))+
  theme(axis.text=element_text(size=10), axis.title=element_text(size=16))

@@

ggplot(combined_reduced,  aes(Year, Documents, colour = DataBase)) +
     geom_line(size = 1, alpha = .80) + 
     facet_wrap(~ Journal) +
  theme_bw() + 
   theme(strip.text.x = element_text(size = 12)) +
  theme(legend.position = "bottom", legend.text = element_text(size = 12)) + 
     scale_colour_discrete(guide = guide_legend(title = "Database"), breaks = c("HD", "Scopus"), labels = c("Historical Database", "Scopus")) + 
  scale_colour_manual(values = c(cp[2], cp[4]), labels = c("Historical Database", "Scopus"), guide = guide_legend(title = "")) + 
  ylab("Number of Articles") + 
  xlab("\nYear") +
     annotate("segment", x = 1992, xend = 1995, y = 140, yend = 140, colour = cp[2], size = 1, alpha = .80) + 
     annotate("segment", x = 1992, xend = 1995, y = 120, yend = 120, colour = cp[4], size = 1, alpha = .80) +
   geom_text(data = scopus_annotate_paper, aes(x = 1999, y =  120, label = label), colour = "black", size = 4) +
  geom_text(data = hd_annotate, aes(x = 1999, y =  140, label = label), colour = "black", size = 4)

@@

(figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + 
    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = Price, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = SWHD, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2016.5, y = 60, label = "3.2% CAGR", size = 5) +
    annotate("text", x = 2016.5, y = 73, label = "Linear growth", size = 5) + 
    annotate("text", x = 2016.5, y = 90, label = "4.7% CAGR", size = 5) + 
    annotate("text", x = 2017.5, y = 65, label = "Observed growth", size = 5) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    #ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19)))
```

@@

#ggsave("figure3.png", figure3, dpi=250)
```

>>>>

@@

small_multiples_paper <- ggplot(combined_reduced,  aes(Year, Documents, colour = DataBase)) +
     geom_line(size = 1, alpha = .80) + 
     facet_wrap(~ Journal) +
  theme_bw() + 
   theme(strip.text.x = element_text(size = 14)) +
  theme(legend.position = "bottom", legend.text = element_text(size = 14)) + 
     scale_colour_discrete(guide = guide_legend(title = "Database"), breaks = c("HD", "Scopus"), labels = c("Historical Database", "Scopus")) + 
  scale_colour_manual(values = c(cp[2], cp[4]), labels = c("Social Work Research Database", "Scopus"), guide = guide_legend(title = "")) + 
  ylab("Number of Articles") + 
  xlab("\nYear") +
     annotate("segment", x = 1992, xend = 1995, y = 140, yend = 140, colour = cp[2], size = 1, alpha = .80) + 
     annotate("segment", x = 1992, xend = 1995, y = 120, yend = 120, colour = cp[4], size = 1, alpha = .80) +
   geom_text(data = scopus_annotate_paper, aes(x = 1999, y =  120, label = label), colour = "black", size = 5) +
  geom_text(data = hd_annotate, aes(x = 1999, y =  140, label = label), colour = "black", size = 5)

ggsave(small_multiples_paper, file = "Figure_1_small_multiples.jpg", dpi = 1200, height = 8, width = 12, units = "in")
```

@@

(figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + 
    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = Price, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = SWHD, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2016.5, y = 60, label = "3.2% CAGR", size = 5) +
    annotate("text", x = 2016.5, y = 73, label = "Linear growth", size = 5) + 
    annotate("text", x = 2016.5, y = 90, label = "4.7% CAGR", size = 5) + 
    annotate("text", x = 2017.5, y = 65, label = "Observed growth", size = 5) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    #ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19)))

ggsave(figure2, file = "figure2.jpeg", width = 7, height = 7, units = "in", dpi = 1200)
```

@@

ggsave(figure3, file = "figure3.jpeg", width = 7, height = 7, units = "in", dpi=1200)
```
